Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-02-01 Master Thesis/synopsis.tex
Small changes

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $(\Gamma':\Gamma)< \infty$ and $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension ([ZS], Ch. VI, §11, Lemma 1 and 2).
\end{proof}

@@

Assume that $w = w_0|_K$ is not henselian. Then there exists a $w_1\in|\operatorname{Spv}(K_0)|$ with $w_1\neq w_0$ and such that $w = w_1|_K$, for otherwise $w$ would have a unique prolongation to $K_0$ and hence to $\overline{K}$ since $w_0$ is henselian.

@@

Now $(K_0)_{w_1}$ is henselian both with respect to $w_1$ and with respect to the prolongation of $w_0$. Lemma \ref{2.2} yields $\operatorname{cd}(G_{(K_0)_{w_1}})\leq 2$, a contradiction. The uniqueness of $w$ is again a consequence of Lemma \ref{2.2}.
\item Choose the prime $\ell$ different from $\operatorname{char} k(w)$ so that (i) holds. According to Lemma \ref{2.5} we have $\operatorname{rrank}(w)=\dim_\mathbb{Q}(\Gamma_w\otimes_\mathbb{Z}\mathbb{Q} )\leq \dim_{\mathbb{F}_\ell}(\Gamma_w /\ell\Gamma_w) = 2$. By Lemma \ref{rank-dimension-inequality}, this inequality is actually an equality. \qedhere
\end{enumerate}
\end{proof}

>>>>

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension ([ZS], Ch. VI, §11, Lemma 1 and 2).
\end{proof}

@@

Assume that $w = w_0|_K$ is not henselian. Then there exists a $w_1\in|\operatorname{Spv}(K_0)|$ with $w_1\neq w_0$ and such that $w = w_1|_K$, for otherwise $w$ would have a unique extension to $K_0$ and hence to $\overline{K}$ since $w_0$ is henselian.

@@

Now $(K_0)_{w_1}$ is henselian both with respect to $w_1$ and with respect to the extension of $w_0$. Lemma \ref{2.2} yields $\operatorname{cd}(G_{(K_0)_{w_1}})\leq 2$, a contradiction. The uniqueness of $w$ is again a consequence of Lemma \ref{2.2}.
\item Choose the prime $\ell$ different from $\operatorname{char} k(w)$ so that (i) holds. According to Lemma \ref{2.5} we have $\operatorname{rrank}(w)=\dim_\mathbb{Q}(\Gamma_w\otimes_\mathbb{Z}\mathbb{Q} )\leq \dim_{\mathbb{F}_\ell}(\Gamma_w /\ell\Gamma_w) = 2$. By Lemma \ref{rank-dimension-inequality}, this inequality is actually an equality. \qedhere
\end{enumerate}
\end{proof}
